A non-additive generalization of probability theory \\for quantum mechanics and beyond

### 2025-07-29 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex
NonAdditiveProbability: adjusting size of figure and caption

	\begin{tikzpicture}[x={(\xx cm, \xy cm)}, y={(\yx cm, \yy cm)}, z={(\zx cm, \zy cm)}, scale=1.3]
		% Bloch sphere (outline drawn in canvas plane)
		\draw (0, 0, 0) circle (\radius cm);

@@

			% meridians and equator
			\begin{scope}[canvas is yz plane at x=0]
				\draw (\ixy, \ixz) arc[start angle={atan2(\ixz, \ixy)}, end angle=90-\stheta, radius=1 cm];
				\draw[dashed] (\ixy, \ixz) arc[start angle={atan2(\ixz, \ixy)}, end angle=\stheta-90, radius=1 cm];
			\end{scope}
			\begin{scope}[canvas is zx plane at y=0]
				\draw[dashed] (\iyz, \iyx) arc[start angle={atan2(\iyx, \iyz)}, delta angle=180, radius=1 cm];
				\draw (-\iyz, -\iyx) arc[start angle={atan2(-\iyx, -\iyz)}, delta angle=180, radius=1 cm];
			\end{scope}
			\begin{scope}[canvas is xy plane at z=0]
				\draw (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, end angle=180-\stheta, radius=1 cm];
				\draw[dashed] (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, end angle=\stheta, radius=1 cm];
			\end{scope}
		\end{scope}
	\end{tikzpicture}
	\caption{...}
\end{figure}

>>>>

	\begin{tikzpicture}[x={(\xx cm, \xy cm)}, y={(\yx cm, \yy cm)}, z={(\zx cm, \zy cm)}, scale=1.2]
		% Bloch sphere (outline drawn in canvas plane)
		\draw (0, 0, 0) circle (\radius cm);

@@

			% meridians and equator
			\begin{scope}[canvas is yz plane at x=0]
				\draw (\ixy, \ixz) arc[start angle={atan2(\ixz, \ixy)}, end angle=90-\stheta, radius=1 cm];
				\draw[dashed] (\ixy, \ixz) arc[start angle={atan2(\ixz, \ixy)}, end angle=\stheta-90, radius=1 cm];
			\end{scope}
			\begin{scope}[canvas is zx plane at y=0]
				\draw[dashed] (\iyz, \iyx) arc[start angle={atan2(\iyx, \iyz)}, delta angle=180, radius=1 cm];
				\draw (-\iyz, -\iyx) arc[start angle={atan2(-\iyx, -\iyz)}, delta angle=180, radius=1 cm];
			\end{scope}
			\begin{scope}[canvas is xy plane at z=0]
				\draw (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, end angle=180-\stheta, radius=1 cm];
				\draw[dashed] (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, end angle=\stheta, radius=1 cm];
			\end{scope}
		\end{scope}
	\end{tikzpicture}
	\caption{For Choquet integral calculation, sets $A(s)$ of all pure states for which the statistical variable is greater than $s$. On the left, the Bloch ball with a plane at constant $s$. On the right, the top case is when the value is greater than the maximum (empty set); the middle case is when the value is in between the target point $\ens[o]$ and the maximum; the third case is when the value is below the target point.}
\end{figure}
